\documentclass[titlepage]{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage[T1]{fontenc}  
\usepackage[utf8]{inputenc}   
\usepackage{geometry}
\usepackage{natbib}
\setcitestyle{authoryear,round,semicolon} 
\usepackage{hyperref}




\usepackage{tabularx,ragged2e,booktabs,caption}
\newcolumntype{C}[1]{>{\Centering}m{#1}}
\renewcommand\tabularxcolumn[1]{C{#1}}
\usepackage[font=small,labelfont=bf]{caption}
 \geometry{
 a4paper,
 total={210mm,297mm},
 left=30mm,
 right=30mm,
 top=30mm,
 bottom=30mm,
 } 
\usepackage{eso-pic}


\renewcommand{\baselinestretch}{1.5} 





\begin{document}
\begin{center}
\section*{Replacement task - Second lecture}
	\subsection*{Lucas Hellström \\ \small{nat14lhe@student.lu.se}}
\end{center}	
		The Academic Writing in English part of the course have improved my way of writing formal English in a few different ways. Overall I think the lecture and the feedback from the assignment made me reflect about how I write and improve my writing. \vspace{0.3cm}
		
		\noindent The main thing I learned is that I should structure my ideas before I started writing. Normally I sit down and write what comes to my mind, that is relatable to the subject, but before starting on writing my thesis I sat down and wrote down what subjects I should include. This helped me a great deal when I started writing as I had an idea of what to include in the thesis.\vspace{0.3cm}
		
		\noindent Another big thing I improved is my use of paragraphs. Before this course I started a new paragraph whenever I thought it fitted in the text. This time I stopped and started to think if that is the correct place to start a new paragraph or if I should wait, or start it earlier to improve the flow of the text. \vspace{0.3cm}
		
		\noindent From the large amount of laboration reports I have written since starting my education in Lund I have developed a style of academic writing that I am satisfied with and thus this course haven't improved my writing in that regard. \vspace{0.3cm}

		\noindent To conclude I am satisfied with the Academic Writing part of the bachelor course. In my opinion the assignment could have been shorted as it took time away from the project but on the other hand if it is too short it may be difficult to get a feel or the writing style of the student. As most physics students in Lund have done laborations here at the University I think that we should be able to submit an old (or new) report from one of the laborations where the English and writing style can be studied from there. It would relieve some of the pressure during the first part of the term where the work load is high due to the project, academic writing, popular science writing and additional courses on top of that. I think that the academic writing part of the course should definitely stay but in my opinion the students should be able to submit a laboration report as the assignment.

\end{document}